Arne report

### 2018-08-11 Report/arne-report.Rmd
Update arne-report.Rmd
Removes unused packages

```{r setup, include=FALSE}
library(ggplot2)
library(ez)
library(Hmisc)
library(dplyr)
library(reshape2)
library(broom)
library(knitr)
library(brainvr.R)
library(restimoter)
library(papaja)

>>>>

```{r setup, include=FALSE}
library(ggplot2)
library(ez)
library(Hmisc)
library(dplyr)
library(reshape2)
library(broom)
library(knitr)
library(papaja)
